---
title: "Getting Started with {golem}"
author: "Colin Fay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a_start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```

## Installing {golem}

`{golem}` can be installed from GitHub using the `{remotes}` package: 

```{r}
remotes::install_github("Thinkr-open/golem")
```

## Getting started 

Note before using `{golem}`: 

- A `{golem}` app is contained inside a package, so knowing how to build a package is highly recommended. 

- A `{golem}` app works better if you are working with `shiny modules`, so knowing how modules work is heavily recommended.

In the rest of the Vignettes, we'll assume you're working in RStudio. 

### Create a package

Once the package is installed, you can got to File > New Project... in RStudio, and choose "Package for Shiny App Using golem" input. 

If you want to do it through command line, you can use:

```{r}
golem::create_golem(path = "path/to/package")
```

This command allows you to create "illegally-named" package (for example, `1234`) by passing the `check_name` argument to `FALSE`. Note that this is not recommanded and __should only be done if you know what you are doing__.

Once you've got that, a new RStudio project will be launched. Here is the structure of this project:

```
DESCRIPTION               
¦--dev/          
  ¦--01_start.R           
  ¦--02_dev.R           
  ¦--03_deploy.R           
  ¦--run_dev.R
¦--inst/ 
  ¦--app                
    ¦--server.R       
    ¦--ui.R           
    ¦--www/          
      ¦--favicon.ico
¦--man/ 
    ¦--run_app.Rd      
NAMESPACE
myapp.Rproj
¦--R/ 
  ¦--app_server.R       
  ¦--app_ui.R           
  ¦--run_app.R      
```
]

If you're already familiar with R pacakges, most of these files will appear very familiar to you. That's because a `{golem}` app IS a package.

+ `DESCRIPTION` & `NAMESPACE`: Package meta-data.

+ `dev/`: Scripts that will be used along the process of developping your app. 

+ `inst/app`: You'll add external dependencies in `www` (images, css, etc). Don't touch `app_ui` and `app_server`.

+ `man`: Package doc, to be generated by R.  

+ `myapp.Rproj`: RStudio project.

+ `R/app_server.R`, `R/app_ui.R`: Top level UI and server elements. 

+ `R/run_app.R`: a function to configure and launch the application.

## `dev/01_start.R`

Once you've created your project, the first file that opens is `dev/01_start.R`. This file contains a series of commands to run once, at the start of the project. 

### Fill the DESC

First, fill the DESCRIPTION by adding information about the package that will contain your app:

```{r eval = FALSE}
golem::fill_desc(
  pkg_name = "shinyexample", # The Name of the package containing the App 
  pkg_title = , # The Title of the package containing the App 
  pkg_description = , # The Description of the package containing the App 
  author_first_name = , # Your First Name
  author_last_name = ,  # Your Last Name
  author_email = ,      # Your Email
  repo_url = NULL)      # The (optional) URL of the GitHub Repo
```

### Set common Files 

If you want to use the MIT licence, README, code of conduct, lifecycle badge, and news

```{r eval = FALSE}
usethis::use_mit_license(name = "Your Name")  # You can set another licence here
usethis::use_readme_rmd()
usethis::use_code_of_conduct()
usethis::use_lifecycle_badge("Experimental")
usethis::use_news_md()
```

### Add a data-raw folder

If you have data in your package

```{r}
usethis::use_data_raw()
```

### Init Tests

Create a template for tests:

```{r}
golem::use_recommended_tests()
```


### Use Recommended Packages

This will add "shiny", "DT", "attempt", "glue", "htmltools", and "golem" as a dependecy to your package.

```{r}
golem::use_recommended_deps("")
```

### Add various tools

These two functions add a file with various functions that can be used along the process of building your app.

See each file in details for a description of the functions.

```{r}
golem::use_utils_ui()
golem::use_utils_server()
```

### If you want to change the default favicon

```{r}
golem::use_favicon( path = "path/to/favicon")
```

## Try the app

To run the app, go to the `dev/run_dev.R` file, and launch the all thing.

You're now set! You've successfully initiated the project and can go to dev/02_dev.R.

```{r}
rstudioapi::navigateToFile("dev/02_dev.R")
```


