---
title: "Day to Day Dev with {golem}"
author: "Colin Fay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{b_dev}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```

## Day to day development with `{golem}`

Now that you're all set with your project init, time to move to development!

App development should happen through the `dev/02_dev.R` file, which contains common commands for developing. 

## Launching the app

To run the app, go to the `dev/run_dev.R` file, and run the all thing.

## `dev/02_dev.R`

### Add dependencies

To be called each time you need a new package as a dependency:

```{r}
usethis::use_package("pkg")
```

About [package dependencies](https://r-pkgs.org/namespace.html).

### Add modules

The `golem::add_module()` functions creates a module in the `R` folder. The file and the modules will be named after the `name` parameter, by adding `mod_` to the R file, and `mod_*_ui` and `mod_*_server` to the UI and server functions.

```{r}
golem::add_module( name = "my_first_module" ) # Name of the module
```

The new file will contain:

```{r}
# mod_UI
mod_my_first_module_ui <- function(id){
  ns <- NS(id)
  tagList(
  
  )
}

mod_my_first_module_server <- function(input, output, session){
  ns <- session$ns
}
    
## To be copied in the UI
# mod_my_first_module_ui("my_first_module_1")
    
## To be copied in the server
# callModule(mod_my_first_module_server, "my_first_module_1")
```

At the end of the file, you will find a piece of code that has to be copied and pasted inside your UI and server functions.

## Add function files 

```{r}
golem::add_fct( "helpers" ) 
golem::add_utils( "helpers" )
```

These two function create `R/fct_helpers.R` and `R/utils_helpers.R`, two file you can use to add business logic functions.

### Add external files

These functions create external dependencies (JavaScript and CSS). `add_js_file()` creates a simple JavaScript file, while `add_js_handler()` adds a file with a skeleton for shiny custom handlers.

```{r}
golem::add_js_file("script")
golem::add_js_handler("script")
golem::add_css_file("custom")
```

Note: While the general philosophy of `{golem}` is being based on the idea that you're building a package, these functions can be used outside of a `{golem}` project. 

Note that you can also download external CSS and JavaScript files with:

```{r}
golem::use_external_css_file(url = "url", name = "your_provided_name")
golem::use_external_js_file(url = "url", name = "your_provided_name")
```

The above has the effect of downloading the file at the specified url and giving it a provided name. If the intent is to use a CDN hosted CSS/JS file then manually add the tag - `tags$script(src = "source_of_ur_css/js")` in the function `golem_add_external_resources` in file `app-ui.R`. 
The tag can be added inside the `tags$head(...)` if the intent is to load the  js/css file in the `<head>` of the document or outside it if it is intended in the `<body>`.

### Adding these external resources to your app

You can add any external resource into `inst/app/www`. 

JavaScript and CSS are automatically linked in the `golem_add_external_resources()` function. If you add other resources (example images), you can link them in the app with the `www` prefix: 

```{r}
tags$img(src = "www/my.png")
```

You can also list here the use of other packages, for example `useShinyalert()` from the `{shinyalert}` package.

### Add a data-raw folder

If you have data in your package: 

```{r}
usethis::use_data_raw()
```

About [data in a package](https://r-pkgs.org/data.html).

### Add tests

Add more tests to your application:

```{r}
usethis::use_test( "app" )
```

About [testing a package](https://r-pkgs.org/tests.html).

## Documentation

### Vignette

```{r}
usethis::use_vignette("shinyexample")
devtools::build_vignettes()
```

About [package Vignette](https://r-pkgs.org/vignettes.html).

### Code coverage

```{r}
usethis::use_travis()
usethis::use_appveyor()
usethis::use_coverage()
```

## Using `{golem}` dev functions

There's a series of tools to make your app behave differently whether it's in dev or prod mode. Notably, the `app_prod()` and `app_dev()` function tests for `options( "golem.app.prod")` (or return TRUE if this option doesn't exist). 

Setting this options at the beginning of your dev process allows to make your app behave in a specific way when you are in dev mode. For example, printing message to the console with `cat_dev()`.

```{r eval = TRUE}
options( "golem.app.prod" = TRUE)
golem::cat_dev("hey\n")
options( "golem.app.prod" = FALSE)
golem::cat_dev("hey\n")
```

You can then make any function being "dev-dependent" with the `make_dev()` function: 

```{r eval = TRUE}
log_dev <- golem::make_dev(log)
log_dev(10)
options( "golem.app.prod" = TRUE)
log_dev(10)
```


