---
title: "c_deploy"
author: "Colin Fay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{c_deploy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## About the `run_app()` function

When launching the app, you might have noticed that the `dev/run_dev.R` function calls `run_app()`, which has the following structure:

```{r}
run_app <- function(...) {
  with_golem_options(
    app = shinyApp(
      ui = app_ui,
      server = app_server
    ),
    golem_opts = list(...)
  )
}
```

This function might looks a little bit weird, but there's a long story behind it, and you can read more about it [there](https://rtask.thinkr.fr/shinyapp-runapp-shinyappdir-difference/).

But long story short, this combination of `with_golem_options` & `golem_opts = list(...)` allows you to pass argument to the function to be used inside the application, from UI or from server side, which you can get with `get_golem_options()`.

```{r}
run_app(this = "that")
# And in the app
this <- get_golem_options("this")
```

The idea is to provide more flexibility for deployment on each platform you want to run your app on.

## Deploying Apps with `{golem}`

The `dev/03_deploy.R` file contains function for deploying on various platforms. 

### RStudio Products

```{r}
golem::add_rstudioconnect_file()
golem::add_shinyappsio_file()
golem::add_shinyserver_file()
```


### Docker 

#### without using {renv}



```{r}
# If you want to deploy via a generic Dockerfile
golem::add_dockerfile()

# If you want to deploy to ShinyProxy
golem::add_dockerfile_shinyproxy()

# If you want to deploy to Heroku
golem::add_dockerfile_heroku()
```

#### using {renv}


#### CASE 1 : you didn't use renv during developpment process


> this functions will create a "deploy" folder containing : 

```
deploy/
+-- Dockerfile
+-- Dockerfile_base
+-- yourgolem_0.0.0.9000.tar.gz
+-- README
\-- renv.lock.prod
```

then follow the README file


```{r}
# If you want to deploy via a generic Dockerfile
golem::add_dockerfile_with_renv(output_dir = "deploy")

# If you want to deploy to ShinyProxy
golem::add_dockerfile_with_renv_shinyproxy(output_dir = "deploy")
```

If you would like to use {renv} during developpement, you can init a renv.lock file with

```{r}
attachment::create_renv_for_dev(dev_pkg = c(
  "renv",
  "devtools",
  "roxygen2",
  "usethis",
  "pkgload",
  "testthat",
  "remotes",
  "covr",
  "attachment",
  "pak",
  "dockerfiler",
  "golem"
))
```
an activate {renv} with

```{r}
renv::activate()
```





#### CASE 2 : you already have a renv.lock file for your project


```{r}

# If you want to deploy via a generic Dockerfile
golem::add_dockerfile_with_renv(output_dir = "deploy", lockfile = "renv.lock")

# If you want to deploy to ShinyProxy
golem::add_dockerfile_with_renv_shinyproxy(output_dir = "deploy", lockfile = "renv.lock")
```

> this functions will create a "deploy" folder containing : 

```
deploy/
+-- Dockerfile
+-- Dockerfile_base
+-- yourgolem_0.0.0.9000.tar.gz
+-- README
\-- renv.lock.prod
```

then follow the README file
