---
title: "Using {golem} js functions"
author: "Colin Fay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{d_js}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/javascript">
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Using `{golem}` js functions

`{golem}` comes with a series of JavaScript functions that you can call from the server. These functions are added by default with `bundle_resources()` .

Then they are called with `golem::invoke_js("fonction", "ui_element")`.

This `ui_element` define the UI element to interact with. It can be a full jQuery selector, an id or a class. Note that you can add several elements and iterate other them.

`invoke_js` can be used with any function defined in a [JavaScript Custom Handler](https://shiny.rstudio.com/articles/communicating-with-js.html#from-r-to-javascript), that you can build with `golem::add_js_handler()`.

### `golem::invoke_js()`

+ `showid` & `hideid`, `showclass` & `hideclass` show and hide elements through their id or class.

```{r eval = FALSE}
golem::invoke_js("showid", ns("plot"))
```

+ `showhref` & `hidehref` hide and show a link by trying to match the `href` content.

```{r eval = FALSE}
golem::invoke_js("showhref", "panel2")
```

+ `clickon` click on the element. You have to use the full jQuery selector. 

+ `show` & `hide` show and hide elements, using the full jQuery selector.

+ `disable` & `reable` able and disable specific element, using the full jQuery selector.

See `?golem::activate_js()` for the full list.

### A quick intro to jQuery selectors

+ `#plop`: the element with the id `plop`

+ `.pouet`: elements of class `pouet`

+ `"button:contains('this')"`: buttons with a text containing `'this'`

Note that in html, tags contains attributes. For example:

``` html
<a href = "https://thinkr.fr" data-value = "panel2">ThinkR</a>
```

contains `href` & `data-value`. You can refer to these attributes with `[]` after the tag name.

+ `a[href = "https://thinkr.fr"]`: link with `href` being `https://thinkr.fr`

+ `a[data-value="panel2"]`: link with  `data-value` being `"panel2"`
