---
title: "Using golem config"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{config}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(golem)
x <- file.path(
  tempdir(), 
  "golex"
)
unlink(x, TRUE, TRUE)

create_golem(x, package_name = "golex", open = FALSE)
knitr::opts_knit$set(root.dir = x)
```

```{r setup}
library(golem)
```

## About `inst/golem-config.yml`

When you start a new `{golem}` application, you'll find a file called `golem-config.yml` in the `inst/` folder. 

By default, this file contains the name of your app, its version, and the default working directory (which is the root of your package). 

This config file is based on the [`{config}`](https://github.com/rstudio/config) format, which allows you to create configuration files for different application contexts. Please refer to this package documentation for more information.

## Setting `golem-config`

Here is what the default config file looks like:

```{r echo = FALSE, comment= ""}
glue::as_glue(
  readLines(
    "inst/golem-config.yml"
  )
)
```

+ default/golem_name, default/golem_version, default/app_prod are usable across the whole life of your golem app: while developing, and also when in production. 
+ production/app_prod might be used for adding elements that are to be used once the app is in production. 
+ dev/golem_wd is in a `dev` config because the only moment you might reliably use this config is while developing your app. Use the `app_sys()` function if you want to rely on the package path once the app is deployed.

The good news is that if you don't want/need to use `{config}`, you can safely ignore this file, __just leave it where it is: it is used internally by the `{golem}` functions__.

These options are globally set with: 

```{r}
set_golem_options()
```

The functions reading the options in this config file are: 

```{r}
get_golem_name()
get_golem_wd()
get_golem_version()
```

You can set these with: 

```{r eval = FALSE}
set_golem_name("this")
set_golem_wd(".")
set_golem_version("0.0.1")
```


## Using `golem-config`

If you're already familiar with the `{config}` package, you can use this file just as any config file. 

`{golem}` comes with an `amend_golem_config()` function to add elements to it.

```{r}
amend_golem_config(
  key = "where", 
  value = "indev"
)
amend_golem_config(
  key = "where", 
  value = "inprod", 
  config = "production"
)
```

Will result in a `golem-config.yml` file as such:

```{r echo = FALSE, comment= ""}
glue::as_glue(
  readLines(
    file.path(x, "inst/golem-config.yml")
  )
)
```

## `app_config.R`

In `R/app_config.R`, you'll find a `get_golem_config()` function that allows you to retrieve config from this config file: 

```{r}
pkgload::load_all()
get_golem_config(
  "where"
)
get_golem_config(
  "where", 
  config = "production"
)
```

Or using the env var (default `{config}` behavior): 

```{r}
Sys.setenv("R_CONFIG_ACTIVE" = "production")
get_golem_config("where")
```

## `golem_config` vs `golem_options`

There is two ways to configure golem apps: 

+ The `golem_opts` in the `run_app()` function 
+ The `golem-config.yml` file
 
The big difference between these two is that the golem options from `run_app()` are meant to be configured during runtime: you'll be doing `run_app(val = "this")`, whereas the `golem-config` is meant to be used in the back-end, and will not be linked to the parameters passed to `run_app()` (even if this is technically possible, this is not the main objective),. 

It's also linked to the `R_CONFIG_ACTIVE` environment variable, just as any `{config}` file. 

The idea is also that the `golem-config.yml` file is shareable across `{golem}` projects (`golem_opts` are application specific), and will be tracked by version control systems. 

## Note for `{golem}` < 0.2.0 users 

If you've built an app with `{golem}` before the version 0.2.0, this config file doesn't exist: you'll be prompted to create it if you update a newer version of `{golem}`. 