---
title: "07. Contribute to Golem"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{07 - Contribute to Golem}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Golem is an open-source project, and we welcome contributions of all kinds.

## Contributing to Golem

Development of {golem} happens on GitHub. You can contribute to the package in several ways:

- **Reporting issues**: If you find a bug, please file a minimal reproducible example on [GitHub](https://github.com/ThinkR-open/golem/issues) with a clear description of the issue.

- **Contributing code**: If you want to contribute code, please open a pull request on [GitHub](https://github.com/ThinkR-open/golem/pulls).

- **Documentation**: If you find a typo or error in the documentation, please open a pull request on [GitHub](https://github.com/ThinkR-open/golem/pulls).

- **Ideas**: If you have an idea for a new feature, please open an issue on [GitHub](https://github.com/ThinkR-open/golem/issues) to discuss it.

Any contribution is welcome!


## Note for the contributors

If you want to contribute to the package, please note that the package is structured as follows:

- The main functions are in the `R/` folder.

- The tests are in the `tests/` folder.

- The documentation is in the `man/` folder.

- The vignettes are in the `vignettes/` folder.

- The Golem template app is in the `inst/shinyexample/` folder.

## Code style

Golem package follows the `grkstyle` style guide. Please make sure to follow the same style when contributing to the package.

If your are using RStudio, you can set the `grkstyle` style guide as the default style guide for the package by running the following code:

``` {r eval=FALSE}
options(
  styler.addins_style_transformer = "grkstyle::grk_style_transformer()"
)
```

If your are using VSCode, you can set the `grkstyle` style guide as the default style guide for the package by running the following code:

``` {r eval=FALSE}
options(languageserver.formatting_style = function(options) {
  grkstyle::grk_style_transformer()
})
```

It's also possible to style one file at a time by running the following code:

``` {r eval=FALSE}
grkstyle::grk_style_file("README.Rmd")
```

## Actual state of the package

The package is in active development. The actual state of the check for `master` is: [![R-CMD-check](https://github.com/ThinkR-open/golem/actions/workflows/R-CMD-check.yaml/badge.svg?branch=master)](https://github.com/ThinkR-open/golem/actions/workflows/R-CMD-check.yaml)

Please make sure that your contribution does not break the package. You can run the checks locally by running the following code:

```{r, eval=FALSE}
devtools::check()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct.html).
By participating in this project you agree to abide by its terms.
